---
title: 'Ch 3: Linear Regression'
author: "Varun Varanasi"
date: "7/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Downloading Packages and Data

```{r}
library(MASS)
library(ISLR)
```

## Working with the Boston Dataset
```{r}
?Boston
```

## Running Simple Linear Regression 
```{r}
lm.fit = lm(medv ~ lstat, data= Boston)
summary(lm.fit)
```

## Retrieving SLR coefficients 

```{r}
names(lm.fit)

coef(lm.fit)
```

## Confidence Intervals
```{r}
confint(lm.fit)
```

## Confidence and Prediction Intervals 
```{r}
predict(lm.fit, data.frame(lstat= c(5,10,15)), interval = "confidence")
```

```{r}
predict(lm.fit, data.frame(lstat= c(5,10,15)), interval = "prediction")
```

## Plotting 
```{r}
attach(Boston)
plot(lstat, medv)
abline(lm.fit)
```

```{r}
par ( mfrow =c(2 ,2) )
plot(lm.fit )
```

```{r}
plot( predict (lm.fit ), residuals (lm.fit ))
plot( predict (lm.fit ), rstudent (lm.fit ))
```
Appears to be some unexplained relationship

## Multiple Linear Regression

```{r}
lm.fit= lm(medv ~ ., data = Boston)
summary(lm.fit)
```


```{r}
library(car)
vif(lm.fit)
```


If we want to remove age

```{r}
lm.fit1 = lm(medv ~ . - age, data=Boston)
```

or alternatively

```{r}
lm.fit1 = update(lm.fit, ~. -age)
```


## Interaction Terms

```{r}
lm_int = lm(medv ~ lstat*age, data = Boston)
summary(lm_int)
```

## Non-linear Transformation

```{r}
lm_trans = lm(medv ~ lstat+ I(lstat^2), data = Boston)
summary(lm_trans)
```


```{r}
lm_slr = lm(medv~lstat, data = Boston)
anova(lm_slr, lm_trans)
```

## Plots

```{r}
par ( mfrow =c(2 ,2) )
plot(lm_trans)
```

## Qualitative Predictors

Using Carsets dataset
```{r}
#fix(Carseats)
names(Carseats)
?Carseats
```

```{r}
lm_fit =lm(Sales~.+ Income : Advertising +Price:Age , data=Carseats)
summary(lm_fit)
```


Find coding used for qualitative variables
```{r}
attach(Carseats)
contrasts(ShelveLoc)
```

